---
title: "Shiny Application and Reproducible Pitch" 
output : ioslides_presentation
date: '`r format(Sys.time(), "%d %B, %Y")`'
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Create a Shiny Application

Files(server.R, ui.R and ShinyApp.Rmd) are available in github repo : 
https://github.com/MALATHI02/DataProducts/tree/master/ShinyApp

Review Criteria:

1.Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

2.Deploy the application on Rstudio's shiny server

3.Share the application link by pasting it into the provided text box

4.Share your server.R and ui.R code on github

## Reproducible Pitch Presentation

Presentation is available in : https://mvakka.shinyapps.io/ShinyAppRep/

Review Criteria:

1.It must be done in Slidify or Rstudio Presenter

2.It must be 5 pages

3.It must be hosted on github or Rpubs

4.It must contained some embedded R code that gets run when slidifying the document

## R Code

```{r, echo = FALSE}

library(shiny)
ui <- shinyUI(pageWithSidebar(
  headerPanel("Household Expenses"),
  sidebarPanel(
    h4('Income (Monthly'),
    numericInput('Income', 'Price ($)', 5000),
    h5('Expenses'),
    numericInput('Grocery', 'Grocery ($ per week)', 200),
    numericInput('CarLoan', 'Car Loan(s) ($ per month)', 180),
    numericInput('Util', 'Utilities ($ per week)', 200),
    numericInput('Cable', 'Cable ($ per month)', 200),
    numericInput('MisExp', 'Miscellaneous expenses ($ per week)', 200)
 ),
  mainPanel(
    h4('Monthly Expenses ($)'),
    textOutput("monExp"),
    h4('Cash Remaining Per Month ($)'),
    textOutput("remBal"),
    br(),
    h4('Instructions'),
    helpText("This application is designed to calculate the potential expenses to income"),
    code("Monthly Expense"),
    helpText("Enter the itemised expenses to calculate the monthly expense."),
    code("Cash Remaining"),
    helpText("This is the Income minus the expenses.")
  )
))

server <- shinyServer(
  function(input, output){
    output$monExp <- renderText({ calculateMonExp(input$Grocery, input$CarLoan,input$Util, input$Cable, input$MisExp) })
    output$remBal <- renderText({(input$Income -(calculateMonExp(input$Grocery, input$CarLoan,input$Util, input$Cable, input$MisExp)) )})

  }
)

calculateMonExp <- function (Grocery, CarLoan,Util,Cable,MisExp)
{
  result <- (Grocery * 4) + CarLoan + Util + Cable + (MisExp * 4)
  expense <- result
  return(round(result, digits = 2))
}

shinyApp(ui, server)
```

## Shiny Application

Link to Application : https://mvakka.shinyapps.io/ShinyApp/

This Application calculates the amount paid for food consumption, utilities and other expenses. The sum of all the expenses is subtracted from income to find the remaining cash on hand.



